### 2019-12-29 overview.tex
figure editting and drop interaction drafting

\bigskip
Imagine the force density ${\bm f}$ in Eq.\ \eqref{eq:Stokes} is singularly supported at the origin, \ie ${\bm f}({\bm x})={\bm F}\delta({\bm x})$, $\delta$ being the Dirac delta, which might be a reasonable approximation to a small sedimenting particle viewed from a distance. Then, the solution of the Stokes equation due to this forcing can be written as
\begin{equation} \label{eq:stokes-green}
 \begin{aligned}
   {\bm u}({\bm x}) = {\bm G}({\bm x}) \cdot {\bm F},
 \end{aligned}
\end{equation}
where  
\begin{equation}
 \begin{aligned}
   {\bm G}({\bm x}) = \frac{1}{8\pi\mu } \bigg( \frac{{\bm I}}{\abs{\bm x}}+\frac{ {\bm r}{\bm r} }{ \abs{{\bm x}}^3 } \bigg),
 \end{aligned}
\end{equation}
is the free-space Green's function, also known as the \emph{Stokeslet}.

Now, if the particle has a finite radius $a$ and the background fluid has a linear velocity ${\bm u}^\infty$ in the absence of the particle, we can perform a Taylor expansion of $\bm G$ and integrate Eq.\ \eqref{eq:stokes-green} over the particle surface to obtain a solution of the following form (in index notation)\footnote{In this simple example, we require the point ${\bm x}$ to be far from the particle so that the terms involving the Green's function can be taken outside the integral, see \cite{graham_2018}.}
\begin{equation} \label{eq:multipole}
 \begin{aligned}
   {u}_i({\bm x})-{u}_i^\infty({\bm x}) = -{G}_{ij}({\bm x}) {F}_j^{d} + \frac{\partial G_{ij}}{\partial x_l}({\bm x}) {D}_{jl} +
   \mathcal{O}\bigg(\frac{a^3}{\abs{{\bm x}}^3}\bigg),
 \end{aligned}
\end{equation}
where ${\bm F}^{d}$ denotes the total drag force exerted on the particle by the fluid, and ${\bm D}$ is an integral expression representing the force dipole.
%\begin{equation} 
% \begin{aligned}
%   {D}_{jl} = \int_{S_p} x'_l n_k \sigma_{kj}({\bm x}') dS({\bm x}').
% \end{aligned}
%\end{equation}
For purposes of analytical calculations, it is customary to decompose ${\bm D}$ into a traceless symmetric part ${\bm S}$, called the \emph{stresslet}, and an antisymmetric part ${\bm R}$, called the \emph{rotlet}, \viz
\begin{subequations}
 \begin{equation}
   {\bm S} = {\bm D}^S - \frac{1}{3} \Tr({\bm D}) {\bm I},
 \end{equation}
 \begin{equation}
  {\bm R} = {\bm D}^A,
 \end{equation}
\end{subequations}
where $D_{ij}^S=(D_{ij}+D_{ji})/2$ and $D_{ij}^A=(D_{ij}-D_{ji})/2$.

The second term on the right-hand side of Eq.\ \eqref{eq:multipole} can then be expressed as
\begin{equation} 
 \begin{aligned}
   \frac{\partial G_{ij}}{\partial x_l}({\bm x}) {D}_{jl} = T_{lij}^{STR}({\bm x}) S_{jl} + T_{lij}^{ROT}({\bm x}) R_{jl},
 \end{aligned}
\end{equation}
where
\begin{subequations}
 \begin{equation}
   T_{jik}^{STR}({\bm x}) = -\frac{1}{8\pi\mu} \frac{3x_i x_j x_k}{\abs{{\bm x}}^5},
 \end{equation}
 \begin{equation}
   T_{jik}^{ROT}({\bm x}) = -\frac{1}{8\pi\mu} \frac{\delta_{ik} x_j - \delta_{ij} x_k}{\abs{{\bm x}}^3}.
 \end{equation}
\end{subequations}

Eq.\ \eqref{eq:multipole} is the \emph{multipole expansion} of the disturbance velocity, ${\bm u}-{\bm u}^\infty$. One immediate physical implication is that a forced particle (\eg a rising bubble) will generate a disturbance that decays as $1/r$, while a force-free particle (\eg a self-propelled bacterium) has a $1/r^2$ decay thus leaving less trace at the same distance away, where $r=\abs{{\bm x}}$. See Figure \ref{fig:lets} for an illustration.\footnote{The rotlet flow is simply a rigid-body rotation centered at the origin.}

\begin{figure}%[t]
  \centering
  \includegraphics[width=0.49\columnwidth]{stokeslet.pdf}
  \includegraphics[width=0.49\columnwidth]{stresslet.pdf}
  \caption{Flow fields due a Stokeslet (left) and a stresslet (right) centered at the origin (red dot). The black arrows display the velocities with their directions indicated by the gray arrows. Note the symmetries and the difference in velocity magnitudes of the two flows.}
  \label{fig:lets}
\end{figure}

Finally, for a sphere of radius $a$, translating with velocity $\bm U$, rotating with angular velocity $\bm \Omega$, its total drag, torque, and stresslet are given by the \emph{Fax\'{e}n's laws},
\begin{subequations} \label{eq:faxen}
 \begin{equation}
   {\bm F}^{d} = 6\pi\mu a\bigg( (1+\frac{a^2}{6}\nabla^2){\bm u^\infty - {\bm U}} \bigg) ,
 \end{equation}
 \begin{equation}
  {\bm T}^{d} = 8\pi\mu a^3 ({\bm \omega}^\infty - {\bm \Omega}),
 \end{equation}
 \begin{equation}
   {\bm S} = \frac{20}{3}\pi\mu a^3 \bigg( 1+\frac{a^2}{10}\nabla^2 \bigg) {\bm E}^\infty ,
 \end{equation}
\end{subequations}
where $\small {\bm E}^\infty=(\nabla {\bm u}^\infty + (\nabla {\bm u}^\infty)^T)/2$ is the rate-of-strain tensor.

@@

\section{Particle interactions}

Batchelor and Green (1972),
swapping,
dancing,
range of interactions,
dipolar theory,
lubrication approximation.
confinement (as another particle)

\section{Rheology}

>>>>

\bigskip
Imagine the force density ${\bm f}$ in Eq.\ \eqref{eq:Stokes} is singularly supported at the origin, \ie ${\bm f}({\bm x})={\bm F}\delta({\bm x})$, $\delta$ being the Dirac delta, which might be a reasonable approximation to a small sedimenting particle viewed from a distance. Then, the solution of the Stokes equation due to this forcing can be written as
\begin{equation} \label{eq:stokes-green}
 \begin{aligned}
   {\bm u}({\bm x}) = {\bm G}({\bm x}) \cdot {\bm F},
 \end{aligned}
\end{equation}
where  
\begin{equation}
 \begin{aligned}
   {\bm G}({\bm x}) = \frac{1}{8\pi\mu } \bigg( \frac{{\bm I}}{\abs{\bm x}}+\frac{ {\bm x}{\bm x} }{ \abs{{\bm x}}^3 } \bigg),
 \end{aligned}
\end{equation}
is the free-space Green's function, also known as the \emph{Stokeslet}.

Now, if the particle has a finite radius $a$ and the background fluid has a linear velocity ${\bm u}^\infty$ in the absence of the particle, we can perform a Taylor expansion of $\bm G$ and integrate Eq.\ \eqref{eq:stokes-green} over the particle surface to obtain a solution of the following form (in index notation)\footnote{In this simple example, we require the point ${\bm x}$ to be far from the particle so that the terms involving the Green's function can be taken outside the integral, see \cite{graham_2018}.}
\begin{equation} \label{eq:multipole}
 \begin{aligned}
   {u}_i({\bm x})-{u}_i^\infty({\bm x}) = -{G}_{ij}({\bm x}) {F}_j^{d} + \frac{\partial G_{ij}}{\partial x_l}({\bm x}) {D}_{jl} +
   \mathcal{O}\bigg(\frac{a^3}{\abs{{\bm x}}^3}\bigg),
 \end{aligned}
\end{equation}
where ${\bm F}^{d}$ denotes the total drag force exerted on the particle by the fluid, and ${\bm D}$ is an integral expression representing a force dipole ($\sim {\bm F}{\bm h}$, $\bm h$ being a separation vector).
%\begin{equation} 
% \begin{aligned}
%   {D}_{jl} = \int_{S_p} x'_l n_k \sigma_{kj}({\bm x}') dS({\bm x}').
% \end{aligned}
%\end{equation}
For purposes of analytical calculations, it is customary to decompose ${\bm D}$ into a traceless symmetric part ${\bm S}$, called the \emph{stresslet}, and an antisymmetric part ${\bm R}$, called the \emph{rotlet}, \viz
\begin{subequations}
 \begin{equation}
   {\bm S} = {\bm D}^S - \frac{1}{3} \Tr({\bm D}) {\bm I},
 \end{equation}
 \begin{equation}
  {\bm R} = {\bm D}^A,
 \end{equation}
\end{subequations}
where $D_{ij}^S=(D_{ij}+D_{ji})/2$ and $D_{ij}^A=(D_{ij}-D_{ji})/2$.

The second term on the right-hand side of Eq.\ \eqref{eq:multipole} can then be expressed as
\begin{equation} 
 \begin{aligned}
   \frac{\partial G_{ij}}{\partial x_l}({\bm x}) {D}_{jl} = T_{lij}^{STR}({\bm x}) S_{jl} + T_{lij}^{ROT}({\bm x}) R_{jl},
 \end{aligned}
\end{equation}
where
\begin{subequations}
 \begin{equation}
   T_{ijk}^{STR}({\bm x}) = -\frac{1}{8\pi\mu} \frac{3x_i x_j x_k}{\abs{{\bm x}}^5},
 \end{equation}
 \begin{equation}
   T_{ijk}^{ROT}({\bm x}) = -\frac{1}{8\pi\mu} \frac{\delta_{jk} x_i - \delta_{ij} x_k}{\abs{{\bm x}}^3}.
 \end{equation}
\end{subequations}

Eq.\ \eqref{eq:multipole} is the \emph{multipole expansion} of the disturbance velocity, ${\bm u}-{\bm u}^\infty$. One immediate physical implication is that a forced particle (\eg a rising bubble) will generate a disturbance that decays as $1/\abs{\bm x}$, while a force-free particle (\eg a self-propelled bacterium) has a $1/\abs{\bm x}^2$ decay thus leaving less trace at the same distance away. See Figure \ref{fig:lets} for an illustration.\footnote{The rotlet flow is simply a rigid-body rotation centered at the origin.}

\begin{figure}%[t]
  \centering
  \includegraphics[width=0.49\columnwidth]{stokeslet1.pdf}
  \includegraphics[width=0.49\columnwidth]{stresslet1.pdf}
  \caption{Flow fields due a Stokeslet (left) and a stresslet (right) centered at the origin (red dot). The black arrows display the velocities, while their directions are also indicated by the gray arrows. The flow fields are both axi- and fore-aft symmetric. Note the difference in the velocity magnitude of the two flows.}
  \label{fig:lets}
\end{figure}

Finally, for a sphere of radius $a$, translating with velocity $\bm U$ and rotating with angular velocity $\bm \Omega$, its total drag, torque, and stresslet are given by the \emph{Fax\'{e}n's laws},
\begin{subequations} \label{eq:faxen}
 \begin{equation}
   {\bm F}^{d} = 6\pi\mu a\bigg( (1+\frac{a^2}{6}\nabla^2){\bm u^\infty - {\bm U}} \bigg) ,
 \end{equation}
 \begin{equation}
  {\bm T}^{d} = 8\pi\mu a^3 ({\bm \omega}^\infty - {\bm \Omega}),
 \end{equation}
 \begin{equation}
   {\bm S} = \frac{20}{3}\pi\mu a^3 \bigg( 1+\frac{a^2}{10}\nabla^2 \bigg) {\bm E}^\infty ,
 \end{equation}
\end{subequations}
where $\small {\bm E}^\infty=(\nabla {\bm u}^\infty + (\nabla {\bm u}^\infty)^T)/2$ is the rate-of-strain tensor.

@@

\section{Droplet interactions}

In practical situations it is seldom the case droplets or particles remain in isolation. They interact with each other through hydrodynamic forces or other applied or physico-chemical interactions.

First let's consider the simplest interaction. Two particles in unbounded linear Stokes flows. Here, linear means ...
\cite{batchelor_green_1972} worked out this case. put their figure here (or a nice one online).
Two modes of interaction: open trajectory (passing) or closed trajectory (rotating).

\cite{Zinchenko1983,Zinchenko1984} showed similar cases for liquid droplets.

With a distant wall, we show possibility of a stationary position.
Also dancing and swapping (\emph{Paper 4}). figure.
Here the wall can be considered as the third particle.

With two walls, \cite{zurita-gotor_2007}
swapping.
We also show static pair under depletion force (\emph{Paper 2}).

even more confined:
dipolar theory \citep{Cui2004,Beatus2006,Janssen2012,Uspal2013,Desreumaux,zhu_gallaire_2016,q2d_Beatus,Diamant},
lubrication approximation.

range of interactions,

\section{Suspension rheology}
